Modelling the emergence of whisker barrels

### 2020-01-29 paper/briefpaper/brief.tex
Fixes a mis-pasted tex error in the manuscript

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) at each We speculate that a projection interacts with a given ephrin field in
the cortical subplate with a strength determined by the concentration of a
similar molecule at its thalamic origin, i.e., the putative barreloid
centerlocation the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii) the branch density of each projection is
conserved over time (Eq.\,\ref{eq:norm}).

The emergence of barrels in simulation required cWe speculate that a projection interacts with a given ephrin field in
the cortical subplate with a strength determined by the concentration of a
similar molecule at its thalamic origin, i.e., the putative barreloid
centerompetition between thalamic
projections in terms of synaptic connectivity and an implicit self/other
identifier amoungst projections, and also competition in terms of cortical
space (as represented by $\chi$). This latter requirement may account for the
absence of
barrels in rodents with larger brains, such as capybara, for which competition
for space is presumably weaker \citep{woolsey_comparative_1975}. Hence,
irrespective of whether barrels are necessary for adaptive whisker function,
the emergence of somatotopically ordered modular structures may be an
inevitable consequence of local competition for cortical territory driven by
input from an array of discrete sensory organs \citep{purves_iterated_1992}.

>>>>

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) at each location the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii) the branch density of each projection is
conserved over time (Eq.\,\ref{eq:norm}).

The emergence of barrels in simulation required competition between thalamic
projections in terms of synaptic connectivity and an implicit self/other
identifier amoungst projections, and also competition in terms of cortical
space (as represented by $\chi$). This latter requirement may account for the
absence of
barrels in rodents with larger brains, such as capybara, for which competition
for space is presumably weaker \citep{woolsey_comparative_1975}. Hence,
irrespective of whether barrels are necessary for adaptive whisker function,
the emergence of somatotopically ordered modular structures may be an
inevitable consequence of local competition for cortical territory driven by
input from an array of discrete sensory organs \citep{purves_iterated_1992}.
